\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex

Figure~\ref{fig:case} shows several screenshots of our Battleship
application. The first screenshot~\ref{fig:player1} shows the board as
viewed by player 1 (note the parameter \texttt{/player1/player1}),
while the second shows the empty board observed when player 2 attempts
to view player 1's board. The screenshot in~\ref{fig:player2strike}
shows the response seen by player 2 upon a successful hit. Finally
screenshot~\ref{fig:player1afterstrike} shows player one's board with
the ship on \bmth{(3,2)} removed.

@@

\section{Conclusion}
\label{sec:conclusion}

asdf asdf

>>>>

Figure~\ref{fig:case} shows several screenshots of our Battleship
application. The first screenshot~\ref{fig:player1} shows the board as
viewed by player 1 (note the parameter \texttt{/player1/player1}),
while the second shows the empty board observed when player 2 attempts
to view player 1's board. The screenshot in~\ref{fig:player2strike}
shows the response seen by player 2 upon a successful hit. Finally
screenshot~\ref{fig:player1afterstrike} shows player one's board with
the ship on \bmth{(2,3)} removed.

@@

\section{Conclusion and Future Work}
\label{sec:conclusion}

In this paper, we have reviewed the operation of faceted execution, a linguistic paradigm
enabling policy-agnostic programming, and showed how it may be implemented within
the Racket programming system as a library of macros. As Racket macros permit core language
forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
to be rewritten arbitrarily, it is possible to rewrite the meaning of these forms to support
a faceted semantics directly. We call our prototype system \racets: Racket with Facets.

The advantage of this approach is that faceted, policy-agnostic, programs may be written
directly in Racket, making use of the wealth of Racket code already available.
A central challenge of this then, is how to ensure there is a sound and practical inter-operation
between racets and standard Racket (or other languages written as libraries in Racket). Our
approach to this has been to use a tagging scheme that identifies values from \racets
so untagged values may be treated by \racets as originating from a non-\racets language.
For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$
form in \racets, can be automatically lifted to support FE (so that it can split when applied
on a faceted value).

Our hypothesis is that this tagging scheme is key to permitting inter-operation
between \racets and Racket, and we have implemented a faceted, web-based game of Battleship
to explore this idea. We suspect that a more thorough investigation of likely idioms
for faceted, non-faceted module interaction is needed and that purely functional code
plays a special role as a degenerate case where arbitrary non-faceted code may be lifted
to operate over facted values without potential unsoundness. In the future, we plan to explore
these design choices in a more principled way and also to scale a static analysis of faceted
execution to fully expanded Racket so it may be applied directly to \racets.
